Introduction

### 2025-05-02 index.qmd
small edit

On this website we list our activities, TG2 publications, further reading and resources, and the members of our topic group.

@@

@@

### Acknowledgements

>>>>

On this website we list topic group specific activities, TG2 publications, further reading and resources, and the members of our topic group.

@@

Find out more about STRATOS at its website: [https://www.stratos-initiative.org](https://www.stratos-initiative.org).

@@

## Acknowledgements
